---
title: "Supplemental Materials II"
format: 
  docx: 
    reference-doc: doc_style_reference.docx
output-file: 'suppmat-2-v1.docx'
---

Notes and Outstanding Issues:


2) I believe that many of the fall soil cover tables have been superseded, including all the Excel sheets starting with "fallcover-soilcover", but this should be confirmed. THEY WERE RERAN, HOW DO THEY LOOK


5) I believe the tables for the perennial weed counts have not been updated since changes were made to the analysis (the denominator degrees of freedom are not what they should be). MAY NEED TO CHECK THIS

6) The table numbering is incorrect, because some tables which I'm not sure what to do the chuck is "turned off", but apparently they still get a number even when the chunk is not evaluated during rendering. So those tables will eventually need to be "turned on" or deleted. TELL SIMON WHEN READY?

```{r}
#| warning: false
#| message: false
#| echo: false

library(knitr)
library(here)
library(readxl)
library(tidyverse)
library(flextable)

opts_chunk$set(fig.align = 'center', echo = F)

set_flextable_defaults(
  post_process_docx = function(ft) flextable::fit_to_width(autofit(ft), 7.25)  # scales down if too wide
)

path = 'data/stats/supp_tables'
```

```{r}
pform = function(x, digits = 4){
  f = function(v, d){
  if (v < 10^(-d)){
    out = paste0('<.', paste(rep('0', d - 1), collapse = ''), '1')
  } else {
    out = sprintf(paste0('%.', d, 'f'), v)
  }
  return(out)
  }
  sapply(x, f, d = digits)
}
```

# Yield

```{r}
#| label: tbl-yield_anova
#| tbl-cap: 'Omnibus tests for factors affecting crop yield'

read_xlsx(here(path, 'yield-anova.xlsx')) |> 
  mutate(`F-value` = round(`F-value`,), 
         `p-value` = pform(`p-value`)) |> 
  flextable() 
```

```{r}
#| label: tbl-yield_emm
#| tbl-cap: 'Estimated marginal mean yields of each cover crop type'

read_xlsx(here(path, 'yield-cc-estimates.xlsx')) |> 
  mutate(across(c(emmean, SE, lower.CL, upper.CL), ~ round(., 2))) |> 
  flextable() 
```

```{r}
#| label: tbl-yield_pairs
#| tbl-cap: 'Pairwise comparisons of yeilds between cover crop types'

read_xlsx(here(path, 'yield-cc-pairwise.xlsx')) |> 
  mutate(across(c(estimate, SE, t.ratio), ~ round(., 2)), 
         p.value = pform(p.value)) |> 
  flextable() 
```

# Fall Biomass

```{r}
#| label: tbl-fall_bio_anova
#| tbl-cap: 'Omnibus tests for factors affecting fall biomass'

read_xlsx(here(path, 'fallbio-anova.xlsx')) |> 
  mutate(F.ratio = round(F.ratio, 1), 
         p.value = pform(p.value)) |> 
  flextable() 
```


```{r}
#| label: tbl-fall_bio_cld
#| tbl-cap: "Estimated marginal means and compact letter display of fall biomass for combinations of cover crop, tillage treatment and year. Treatments within a year not sharing any common letters are statistically significantly different (Sidak adjusted p < 0.05)"

read_xlsx(here(path, "fallbio-letters.xlsx")) |> 
  mutate(across(c(emmean, SE, lower.CL, upper.CL), ~ round(., 2))) |> 
  rename(group = .group) |> 
  flextable() 
```

# Fall Soil Cover

```{r}
#| label: tbl-fall_cover_cc_anova
#| tbl-cap: 'Omnibus tests of factors affecting fall soil cover'

read_xlsx(here(path, 'fallcover-cc-anova.xlsx')) |> 
  mutate(Chisq = round(Chisq, 1), 
         p.value = pform(p.value)) |> 
  dplyr::select(`model term`, Chisq, df1, p.value) |> 
  rename('\u03c7\u00b2' = Chisq, 
         df = df1) |>
  flextable() 
```

```{r}
#| label: tbl-fall_cover_cc_emms
#| tbl-cap: 'Estimated marginal mean fall soil cover for each cover crop'
read_xlsx(here(path, 'fallcover-cc-cc-estimates.xlsx')) |> 
  mutate(across(c(response, SE, asymp.LCL, asymp.UCL), ~ round(., 3))) |> 
  flextable() 
```

```{r}
#| label: tbl-fall_cover_ccwea_pairs
#| tbl-cap: 'Pairwise comparisons between years of fall soil cover for each cover crop'

# The way these comparisons were performed was statistically very inefficient
# and I suggest we revise lines 191-198 in 01_fallcover-linearmodels-cc.R
read_xlsx(here(path, 'fallcover-cc-ccwea-pairs.xlsx')) |> 
  rename(log.odds.ratio = estimate, cctrt = cctrt1) |> 
  mutate(contrast = paste0(w1, ' - ', w2),
         across(c(log.odds.ratio, SE, z.ratio), ~ round(., 2)), 
         p.value = pform(p.value)) |>
  dplyr::select(contrast, cctrt, log.odds.ratio, SE, z.ratio, p.value) |> 
  flextable() 
```

```{r}
#| label: tbl-fall_cover_anova_old
#| tbl-cap: 'Omnibus tests of factors affecting fall soil cover'
#| eval: false
# I'm fairly certain that this table has beeen superceded and should
# not be included in the supplemental materials.
read_xlsx(here(path, 'fallcover-soilcover-anova.xlsx')) |> 
  mutate(statistic = round(statistic, 1), 
         p.value = pform(p.value)) |> 
  rename('\u03c7\u00b2' = statistic) |> 
  flextable() 
```

```{r}
#| label: tbl-fall_cover_till_emms_old
#| tbl-cap: 'Estimated marginal mean fall soil cover for combinations of cover crop and tillage treatment'
#| eval: false
# I'm fairly certain that this table has beeen superceded and should
# not be included in the supplemental materials.
read_xlsx(here(path, 'fallcover-soilcover-cctill-estimates.xlsx')) |> 
  mutate(across(c(response, SE, asymp.LCL, asymp.UCL), ~ round(., 3))) |> 
  flextable() 
```

```{r}
#| label: tbl-fall_cover_till_pairs_old
#| tbl-cap: 'Pairwise comparisons between tillage treatments of fall soil cover for each cover crop treatment'
#| eval: false
# I'm fairly certain that this table has beeen superceded and should
# not be included in the supplemental materials.
read_xlsx(here(path, 'fallcover-soilcover-cctill-pairs.xlsx')) |> 
  mutate(across(c(odds.ratio, SE, z.ratio), ~ round(., 2)), 
         p.value = pform(p.value)) |> 
  dplyr::select(-null) |> 
  flextable() 
```

```{r}
#| label: tbl-fall_cover_year_emms_old
#| tbl-cap: 'Estimated marginal mean fall soil cover for each year'
#| eval: false
# I'm fairly certain that this table has beeen superceded and should
# not be included in the supplemental materials.
read_xlsx(here(path, 'fallcover-soilcover-wea-estimates.xlsx')) |> 
  mutate(across(c(response, SE, asymp.LCL, asymp.UCL), ~ round(., 3))) |> 
  flextable() 
```

```{r}
#| label: tbl-fall_cover_yearcc_pairs
#| tbl-cap: 'Pairwise comparisons between years of fall soil cover for each cover crop treatment'
#| eval: false
# I'm fairly certain that this table has beeen superceded and should
# not be included in the supplemental materials.
read_xlsx(here(path, 'fallcover-soilcover-weacc-pairs.xlsx')) |> 
  mutate(across(c(odds.ratio, SE, z.ratio), ~ round(., 2)), 
         p.value = pform(p.value)) |> 
  dplyr::select(-null) |> 
  flextable() 
```

```{r}
#| label: tbl-fall_cover_ccyear_pairs_old
#| tbl-cap: 'Pairwise comparisons between cover crops of fall soil cover for each year'
#| eval: false
# I'm fairly certain that this table has beeen superceded and should
# not be included in the supplemental materials.
read_xlsx(here(path, 'fallcover-soilcover-ccwea-pairs.xlsx')) |> 
  mutate(across(c(odds.ratio, SE, z.ratio), ~ round(., 2)), 
         p.value = pform(p.value)) |> 
  dplyr::select(-null) |> 
  flextable() 
```

# Fall Vegetation Community

```{r}
#| label: tbl-fall_community_anova
#| tbl-cap: 'Permutational multivariate ANOVA of fall vegetation cover communities'

read_xlsx(here(path, 'fallcommunity-anova-onemodel.xlsx')) |> 
  mutate(across(c(SumOfSqs, statistic), ~round(., 1)), 
         R2 = round(R2, 2), 
         p.value = ifelse(is.na(p.value), NA, '<.001')) |>
  flextable() 
```


# Spring Weed Abundance

```{r}
#| label: tbl-spring_count_anova
#| tbl-cap: 'Omnibus tests for factors affecting spring weed abundance'

read_xlsx(here(path, 'spweedcounts-anova.xlsx')) |>
  dplyr::select(`model term`, df1, Chisq, p.value) |> 
  mutate(Chisq = round(Chisq, 1), 
         p.value = pform(p.value)) |>
  rename('\u03c7\u00b2' = Chisq) |> 
  flextable() 
```

```{r}
#| label: tbl-spring_count_cctillyear_emms
#| tbl-cap: 'Estimated marginal mean weed abundance for each combination of tillage treatment, cover crop, and year'

read_xlsx(here(path, 'spweedcounts-cctillyear-estimates.xlsx')) |>
  mutate(across(c(response, SE, asymp.LCL, asymp.UCL), ~round(., 1))) |>
  flextable() 
```

```{r}
#| label: tbl-spring_count_cctillyear_pairs
#| tbl-cap: 'Pairwise comparisons of weed abundance between cover crop types for each combination of tillage treatment and year'

read_xlsx(here(path, 'spweedcounts-cctillyear-pairs.xlsx')) |>
  mutate(across(c(ratio, SE, z.ratio), ~round(., 2)), 
         p.value = pform(p.value)) |>
  dplyr::select(-null, -df) |> 
  flextable() 
```

```{r}
#| label: tbl-spring_count_strawyear_pairs
#| tbl-cap: 'Pairwise comparisons of weed abundance between straw treatments for each year'

read_xlsx(here(path, 'spweedcounts-strawyear-pairs.xlsx')) |>
  mutate(across(c(ratio, SE, z.ratio), ~round(., 2)), 
         p.value = pform(p.value)) |>
  dplyr::select(-null, -df) |> 
  flextable() 
```

# Spring Species Richness

```{r}
#| label: tbl-spring_rich_cc_ests
#| tbl-cap: 'Estimated marginal mean total species richness for each cover crop type'

read_xlsx(here(path, 'spnu-cc-estimates.xlsx')) |>
  mutate(across(c(rate, SE, asymp.LCL, asymp.UCL), ~round(., 2))) |>
  flextable() 
```

```{r}
#| label: tbl-spring_rich_year_emm
#| tbl-cap: 'Estimated marginal mean total species richness for each year'
read_xlsx(here(path, 'spnu-year-estimates.xlsx')) |>
  mutate(across(c(rate, SE, asymp.LCL, asymp.UCL), ~round(., 2))) |>
  flextable() 
```

```{r}
#| label: tbl-spring_perenn_richness_anova
#| tbl-cap: 'Omnibus tests for factors affecting spring perennial weed species richness'

read_xlsx(here(path, 'spweedcountsPERENN-anova.xlsx')) |>
  dplyr::select(`model term`, df1, df2, F.ratio, p.value) |> 
  mutate(F.ratio = round(F.ratio, 1), 
         p.value = pform(p.value)) |>
  flextable() 
```

```{r}
#| label: tbl-spring_perenn_rich_till_emm
#| tbl-cap: 'Estimated marginal mean perennial species richness for each tillage treatment'
read_xlsx(here(path, 'spweedcountsPERENN-till-estimates.xlsx')) |>
  mutate(across(c(response, SE, lower.CL, upper.CL), ~round(., 2))) |>
  dplyr::select(-weed_type2) |> 
  flextable() 
```

```{r}
#| label: tbl-spring_perenn_rich_till_pairs
#| tbl-cap: 'Pairwise comparisons of perennial species richness between tillage treatments for each combination of cover crop and straw treatment'
read_xlsx(here(path, 'spweedcountsPERENN-till-pairs.xlsx')) |>
  dplyr::select(-weed_type2) |> 
  mutate(across(c(estimate, SE, t.ratio), ~round(., 2)), 
         p.value = pform(p.value)) |>
  flextable() 
```


```{r}
#| label: tbl-spring_perenn_rich_cc_pairs
#| tbl-cap: 'Pairwise comparisons of perennial species richness between cover crops for each combination of tillage and straw treatment'
read_xlsx(here(path, 'spweedcountsPERENN-cc-pairs.xlsx')) |>
  dplyr::select(-weed_type2, -p.val_highlight) |> 
  mutate(across(c(estimate, SE, t.ratio), ~round(., 2)), 
         p.value = pform(p.value)) |>
  flextable() 
```
